\Large\textsc{Regression And Resampling Techniques \\ FYS-STK4155 \\ Assignment One}

### 2019-09-24 assignment_one/article/main.tex
Working on table

\usepackage[]{mathtools}
\usepackage[]{amssymb}
\usepackage[]{libertine}
\usepackage[]{libertinust1math}
\usepackage[T1]{fontenc}
\usepackage[]{microtype}
\usepackage[]{geometry}
\usepackage[]{amsthm}
\usepackage[]{thmtools}
\usepackage[usedvipsnames]{xcolor}
\usepackage[]{bm}
\usepackage[]{amsmath}
\usepackage[]{commath}
\usepackage[]{todonotes}
\usepackage[]{graphicx}
\usepackage{titling}
\usepackage{mdframed}
\usepackage[]{FiraMono}
\usepackage[]{FiraSans}

@@

  We sample \( N = 1000 \) points in each parameter direction and compute the
  corresponding \( N^2 \) funciton values of the Franke function both with and
  without added noise. The noise was selected to be distributed as \( \N(0,
  1) \) with a signal-to-noise ratio \( \alpha = 0.05\).

@@

  \begin{table}
    \caption{}
    \label{tab:ols_confidence}
  \end{table}
  \section{Terrain Data}

>>>>

\usepackage[]{mathtools}
\usepackage[]{amssymb}
%\usepackage[]{libertine}
%\usepackage[]{libertinust1math}
\usepackage[]{mathpazo}
\usepackage[]{eulervm}
\usepackage[T1]{fontenc}
\usepackage[]{microtype}
\usepackage[]{geometry}
\usepackage[]{amsthm}
\usepackage[]{thmtools}
\usepackage[usedvipsnames]{xcolor}
\usepackage[]{bm}
\usepackage[]{amsmath}
\usepackage[]{commath}
\usepackage[]{todonotes}
\usepackage[]{graphicx}
\usepackage{titling}
\usepackage{mdframed}
\usepackage[]{FiraMono}
\usepackage[]{FiraSans}
\usepackage[]{siunitx}

@@

  We sample \( N = 1000 \) points in each parameter direction and compute the
  corresponding \( N^2 \) function values of the Franke function both with and
  without added noise. The noise was selected to be distributed as \( \N(0,
  1) \) with a signal-to-noise ratio \( \alpha = 0.05\).

@@

  \begin{table}
		\begin{tabular}{llllllr}
	\toprule
	{\(d\)} &         0 &         1 &         2 &         3 &         4 &         5 \\
	\midrule
	$1$       & \num{1.030e-05} & \num{2.010e-05} & \num{5.315e-05} & \num{6.349e-05} & \num{7.072e-05} & \num{6.696e-05} \\[1em]
	$x$       &       {} & \num{3.435e-05} & \num{4.673e-04} & \num{1.682e-03} & \num{4.398e-03} & \num{8.402e-03} \\
	$y$       &       {} & \num{3.435e-05} & \num{4.673e-04} & \num{1.683e-03} & \num{4.396e-03} & \num{8.400e-03} \\[1em]
	$x^2$     &       {} &       {} & \num{3.686e-04} & \num{6.458e-03} & \num{4.694e-02} & \num{1.959e-01} \\
	$x y$     &       {} &       {} & \num{2.948e-04} & \num{4.106e-03} & \num{2.873e-02} & \num{1.195e-01} \\
	$y^2$     &       {} &       {} & \num{3.686e-04} & \num{6.460e-03} & \num{4.692e-02} & \num{1.959e-01} \\[1em]
	$x^3$     &       {} &       {} &       {} & \num{2.575e-03} & \num{8.868e-02} & \num{9.884e-01} \\
	$x^2 y$   &       {} &       {} &       {} & \num{1.985e-03} & \num{5.199e-02} & \num{5.432e-01} \\
	$x y^2$   &       {} &       {} &       {} & \num{1.985e-03} & \num{5.199e-02} & \num{5.429e-01} \\
	$y^3$     &       {} &       {} &       {} & \num{2.575e-03} & \num{8.864e-02} & \num{9.884e-01} \\[1em]
	$x^4$     &       {} &       {} &       {} &       {} & \num{2.084e-02} & \num{1.078e+00} \\
	$x^3 y$   &       {} &       {} &       {} &       {} & \num{1.585e-02} & \num{6.287e-01} \\
	$x^2 y^2$ &       {} &       {} &       {} &       {} & \num{1.528e-02} & \num{5.443e-01} \\
	$x y^3$   &       {} &       {} &       {} &       {} & \num{1.585e-02} & \num{6.285e-01} \\
	$y^4$     &       {} &       {} &       {} &       {} & \num{2.083e-02} & \num{1.078e+00} \\[1em]
	$x^5$     &       {} &       {} &       {} &       {} &       {} & \num{1.658e-01} \\
	$x^4 y$   &       {} &       {} &       {} &       {} &       {} & \num{1.253e-01} \\
	$x^3 y^2$ &       {} &       {} &       {} &       {} &       {} & \num{1.193e-01} \\
	$x^2 y^3$ &       {} &       {} &       {} &       {} &       {} & \num{1.192e-01} \\
	$x y^4$   &       {} &       {} &       {} &       {} &       {} & \num{1.253e-01} \\
	$y^5$     &       {} &       {} &       {} &       {} &       {} & \num{1.658e-01} \\
	\bottomrule
	\end{tabular}
	\caption{The variance of the model parameters \( beta \) with respect
		to the polynomial degree \( d \). The corresponding basis
		function is displayed to the left. Note in particular how the
		variance of the model parameters seems to increase with the
		polynomial degree, which is what is to be expected according to
	the \emph{bias-variance tradeoff}.}
    \label{tab:ols_confidence}
  \end{table}

  \subsubsection{Ridge and Lasso regression}

  We now incorporate Ridge and Lasso regression in our numerical experiments.
  We are still working with the noisy sampled data.

  \section{Terrain Data}
